\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-11 adaptive-estimation.tex
fixed proof of Theorem 4
Working on proof of SGD

\section{Adaptive Estimation \label{sec:sequential}}
The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$. We also provide a particular adaptive estimation scheme that attains this maximal efficiency. %Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages. %Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.

\subsection{Limited efficiency in the adaptive setting}
Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
\[
n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
\]
where 
\[
I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
\]
is the Fisher information with respect to a location model in $\theta$. 
\end{thm}

\subsubsection*{Proof}
%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$. The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$. The details are in
See Appendix~\ref{proof:thm:adpative_lower_bound}.\par

Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
\[
n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
\]
and 
\[
\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
\]
It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}. See also \cite{DBLP:journals/corr/abs-1902-08582}. \par
%
Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.

\subsection{Asymptotically optimal estimator}
Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
\begin{equation}
\label{eq:sgd_alg}
\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
\end{equation}
where 
\begin{equation}
B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
\end{equation}
Define the $n$th step estimation as
\begin{equation} \label{eq:sgd_est}
\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
\end{equation}

We have the following results:
\begin{thm} \label{thm:sgd}
Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
\begin{enumerate}
\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
\begin{equation} \label{eq:conditions1}
\begin{cases}
\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
\mathrm{for~some~}0< \lambda \leq 1
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
\[
\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
\]
%
%
\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite Fisher information 
\[
\sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
\]
for the location in the family $\{P_\theta\}$.
%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
Then for any bounded, symmetric, and quasi-convex function $L$, 
\begin{align} 
& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
\\
& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
\end{align}
where $Z \sim \Ncal(0,1)$. 
%
%
\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
\begin{equation} \label{eq:conditions2}
\begin{cases}
\gamma_n = o(n^{-2/3}), &  \\
\sum_{n=1}^\infty \gamma_n = \infty.  & \\
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
\[
 \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
\]
\end{enumerate}
\end{thm}

\subsubsection*{Proof}
See Appendix~\ref{proof:thm:sgd}. \par

@@

\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
\[
B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
\]
and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
%
We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once. 
%
In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$. Figure~\ref{fig:one_round} illustrates a diagram of this procedure. 
%
The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
\begin{thm}
For $i=1,\ldots,n$ set
\[
B_i = \begin{cases}
 \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
 \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
\end{cases}
\]
where $n = n_1+ n_2$ and 
\[
{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
 \right).
\] 
Let 
\[
{\theta}_{n_2}  \triangleq {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
\]
and assume that, as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_2(n)/n \rightarrow 1$. Then:
\begin{align*}
 \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
\end{align*}
\end{thm}
%
%
\begin{proof}
For $t\in \mathbb R$, set
\[
p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
\]
Since $n_2(n)/n \to 1$, if follows from the Berry Esseen theorem that there exists $C$, independent of $n$ and $t$, such that 
\begin{align*}
\sup_{t \in \R} \left| \sqrt{n} \frac{ p_{n_2}(t) - F( \theta - t)} {F(\theta - t) F \left( t - \theta\right) }  - \Phi(t) \right|  \leq C/\sqrt{n}. 
\end{align*}
where $Z \sim \Ncal(0,1)$. It follows that
\begin{align}
\label{eq:two_step_proof}
 \sqrt{n} \frac{ p_{n_2}(Y_n) - F(0)} {F^2(0) }  \overset{d}{\rightarrow} \Ncal(0,1)
\end{align}
for any sequence of random variables $\{Y_n\}$ converging in probability to $\theta$. In particular, since
\[
p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
\]
by the law of large numbers, \eqref{eq:two_step_proof} holds with $Y_n = \theta_{n_1}$. Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
\begin{align*}
& \sqrt{n}\left( \theta_{n_2} - \theta \right) = \sqrt{n} \left( \theta_{n_1} + F^{-1}(p_{n_2}(\theta_{n_1})) - \theta \right) \\
&= \sqrt{n} \left( g(p_{n_2}(\theta_{n_1})) - g \left(F(\theta-\theta_{n_1}) \right)  \right) \overset{d}{\to} \Ncal\left(0, 
F^2(0)/ f^2(0) \right).
\end{align*}
\end{proof}
%

>>>>

\section{Adaptive Estimation \label{sec:sequential}}

The first main result of this paper (Theorem~\ref{thm:adpative_lower_bound})
gives that the asymptotic variance of any adaptive estimator must be at
least $\eta(0)\sigma^2$, which is precisely the efficiency of the median of
the sample $X_1,\ldots,X_n$. Conveniently, the stochastic (sub)gradient
estimator for the median---which minimizes $\E[|X - \theta|]$---is a
sequence of signs (single bits), so that we can exhibit an asymptotically
optimal adaptive estimation scheme.

%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages. %Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.

We begin with our first theorem, whose proof we provide in
Appendix~\ref{proof:thm:adpative_lower_bound}.
\begin{thm}[Fundamental limits]\label{thm:adpative_lower_bound}
  Let Assumption~\ref{assump:failure_rate} hold.
  Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of
  Figure~\ref{fig:setup}(ii). Assume that the prior
  density $\pi(\cdot)$ on $\theta$ converges to zero
  at the endpoints of the interval $\Theta$ and
  define the prior Fisher information
  $I_0 \defeq \E_\pi[(\pi'(\theta) / \pi(\theta))^2]$.
  Then
  \begin{equation*}
    n \E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0}.
  \end{equation*}
\end{thm}

%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$. The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$. The details are in

%% Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
%% \begin{equation*}
%% n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
%% \end{equation*}
%% and 
%% \begin{equation*}
%% \ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
%% \end{equation*}
It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other
loss functions using a more subtle version of the Van Trees
inequality~\cite{efroimovich1980information}; see also
\cite{DBLP:journals/corr/abs-1902-08582}.

We now turn to asymptotically optimal estimators, first
showing how a simple stochastic gradient scheme is asymptotically
optimal (in the fully adaptive setting), after which we show that
a one-round adaptive scheme can also achieve this optimal efficiency.

\subsection{Asymptotically optimal estimator}

The starting point for our first estimator is to note that the median of a
distribution minimizes $\E[|X - \theta|]$ over $\theta \in \R$, and
moreover, we have the familiar result (cf.~\cite{VanDerVaart98}, Ch.~21)
that given a sample $X_1^n \simiid P$, if $\theta = \mbox{med}(P)$ and
$P$ has density $f$ near $\theta$, then
\begin{equation*}
  \sqrt{n}(\mbox{med}(X_1^n) - \theta)
  \cd \normal\left(0, \frac{1}{4 f(\theta)^2}\right),
\end{equation*}
which is precisely the variance lower bound in
Theorem~\ref{thm:adpative_lower_bound}.  Thus, it it is natural consider a
stochastic gradient procedure for minimizing $\E[|X - \theta|]$. To that end,
let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive
sequence of stepsizes,
and define the sequence
\begin{equation}
  \label{eq:sgd_alg}
  \theta_n = \theta_{n-1} + \gamma_n B_n, \quad n = 1,2,\ldots,
\end{equation}
where 
\begin{equation*}
  B_n = \sgn (X_n - \theta_{n-1}).
\end{equation*}
We make one of two assumptions on the stepsizes $\gamma_n$, which
are relatively standard: we always have $\gamma_n$ non-increasing, and
\begin{subequations}
  For some $0 < \lambda \le 1$,
  \begin{align}
    \label{eqn:lazy-gamma}
    \frac{\gamma_n - \gamma_{n+1}}{\gamma_n^2}
    \to 0, & ~~~
    \sum_n \frac{\gamma_n^\frac{1 + \lambda}{2}}{\sqrt{n}} < \infty
    ~~ \mbox{or} \\
    \gamma_n = o(n^{-2/3}),
    & ~~~
    \sum_n \gamma_n = \infty.
    \label{eqn:stringent-gamma}
  \end{align}
\end{subequations}

Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
on the asymptotic normality of averaged stochastic gradient estimators
to establish the following theorem.
\begin{thm}
  \label{thm:sgd}
  Define the average $\bar{\theta}_n \defeq \frac{1}{n}
  \sum_{i = 1}^n \theta_i$. Assume
  that in a neighborhood
  of $\theta = \mbox{med}(P)$,
  the distribution $P$ has a Lipschitz continuous density $f$.
  Then
  \begin{enumerate}[(i)]
  \item \label{item:normal-sgd}
    Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
    Then
    \begin{equation*}
      \sqrt{n}\left( \bar{\theta}_n - \theta\right)
      \cd \normal\left(0,\frac{1}{4 f(\theta)^2}\right).
    \end{equation*}
    %
    %
  \item
    Assume in addition that $f(x)$ is continuously differentiable with a
    finite Fisher information
    \begin{equation*}
      \sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
    \end{equation*}
    for the location in the family $\{P_\theta\}$.
    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
    Then for any bounded, symmetric, and quasi-convex function $L$, 
    \begin{align} 
      & \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
      \\
      & \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
    \end{align}
    where $Z \sim \Ncal(0,1)$. 
    %
    %
  \item Assume the stepsizes $\gamma_n$ satisfy both
    conditions~\eqref{eqn:lazy-gamma} and~\eqref{eqn:stringent-gamma}.
    Then
    \begin{equation*}
      \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{4 n f(\theta)^2} + o(n^{-1}). 
    \end{equation*}
  \end{enumerate}
\end{thm}

\noindent
We provide the proof in Appendix~\ref{proof:sgd}.

As an immediate corollary to Theorem~\ref{thm:sgd}, we obtain the following
asymptotic optimality results of the averaged stochastic gradient
sequence.
%% \begin{corollary}

\textbf{FILL THIS IN}

%% \end{corollary}

@@

\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
\begin{equation*}
B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
\end{equation*}
and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
%
We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once. 
%
In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$. Figure~\ref{fig:one_round} illustrates a diagram of this procedure. 
%
The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
\begin{thm}
For $i=1,\ldots,n$ set
\begin{equation*}
B_i = \begin{cases}
 \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
 \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
\end{cases}
\end{equation*}
where $n = n_1+ n_2$ and 
\begin{equation*}
{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
 \right).
\end{equation*} 
Let 
\begin{equation*}
{\theta}_{n_2}  \triangleq {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
\end{equation*}
and assume that, as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_2(n)/n \rightarrow 1$. Then:
\begin{align*}
 \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
\end{align*}
\end{thm}
%
%
\begin{proof}
For $t\in \mathbb R$, set
\begin{equation*}
p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
\end{equation*}
Since $n_2(n)/n \to 1$, if follows from the Berry Esseen theorem that there exists $C$, independent of $n$ and $t$, such that 
\begin{align*}
\sup_{t \in \R} \left| \sqrt{n} \frac{ p_{n_2}(t) - F( \theta - t)} {F(\theta - t) F \left( t - \theta\right) }  - \Phi(t) \right|  \leq C/\sqrt{n}. 
\end{align*}
where $Z \sim \Ncal(0,1)$. It follows that
\begin{align}
\label{eq:two_step_proof}
 \sqrt{n} \frac{ p_{n_2}(Y_n) - F(0)} {F^2(0) }  \overset{d}{\rightarrow} \Ncal(0,1)
\end{align}
for any sequence of random variables $\{Y_n\}$ converging in probability to $\theta$. In particular, since
\begin{equation*}
p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0)
\end{equation*}
by the law of large numbers, \eqref{eq:two_step_proof} holds for $Y_n = \theta_{n_1}$. Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
\begin{align*}
& \sqrt{n}\left( \theta_{n_2} - \theta \right) = \sqrt{n} \left( \theta_{n_1} + F^{-1}(p_{n_2}(\theta_{n_1})) - \theta \right) \\
&= \sqrt{n} \left( g(p_{n_2}(\theta_{n_1})) - g \left(F(\theta-\theta_{n_1}) \right)  \right) \overset{d}{\to} \Ncal\left(0, 
F^2(0)/ f^2(0) \right).
\end{align*}
\end{proof}
%

### 2019-12-11 problem-formulation.tex
Working on proof of SGD

For $f$ the normal density, classical results~\cite{Samford1953,
  hammersley1950estimating} show that that $\eta(x)$ is a strictly
decreasing function of $|x|$, as we illustrate in Fig.~\ref{fig:eta}.
%
We consider log-concave symmetric distributions sharing this
property.  Specifically, we require the following.
\begin{assumption} \label{assump:failure_rate}
  The origin $x = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is
  non-increasing in $|x|$.
\end{assumption}
Under this assumption,
\begin{equation*}
  4 f^2(x) \leq \eta(x) \leq \eta(0),
\end{equation*} 
%
where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median
(Eq.~\eqref{eqn:variance-quantiles} at $p = 1/2$).  Combined with
log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that
$\eta(x)$ vanishes as $|x|\rightarrow \infty$.  Several distributions
satisfy Assumption~\ref{assump:failure_rate}, including the generalized
normal distributions with a shape parameter between $1$ and $2$ (including
the normal and Laplace distributions). Symmetric log-concave distributions
that failing Assumption~\ref{assump:failure_rate} include the uniform
distribution and the generalized normal distribution with shape parameter
greater than $2$. (See Appendix~\ref{sec:uniform-weirdos} for
a brief discussion on the uniform distribution, which illustrates
why some restriction of the class of distributions is necessary to
develop our results; in brief, even one-step adaptive estimators
with a single bit can achieve rates faster than the paramateric
$\sqrt{n}$ convergence for location estimation in the uniform distribution.)

>>>>

For $f$ the normal density, classical results~\cite{Samford1953,
  hammersley1950estimating} show that that $\eta(x)$ is a strictly
decreasing function of $|x|$, as we illustrate in Fig.~\ref{fig:eta}.
%
We consider log-concave symmetric distributions sharing this
property.  Specifically, we require the following.
\begin{assumption}
  \label{assump:failure_rate}
  The density $f$ is log-concave and symmetric.  Additionally, the origin $x
  = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is non-increasing in
  $|x|$.
\end{assumption}
Under this assumption,
\begin{equation*}
  4 f^2(x) \leq \eta(x) \leq \eta(0),
\end{equation*} 
%
where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median
(Eq.~\eqref{eqn:variance-quantiles} at $p = 1/2$).  Combined with
log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that
$\eta(x)$ vanishes as $|x|\rightarrow \infty$.  Several distributions
satisfy Assumption~\ref{assump:failure_rate}, including the generalized
normal distributions with a shape parameter between $1$ and $2$ (including
the normal and Laplace distributions). Symmetric log-concave distributions
failing Assumption~\ref{assump:failure_rate} include the uniform
distribution and the generalized normal distribution with shape parameter
greater than $2$. Some restriction on the class of distributions is
necessary to develop our results; indeed, in
Appendix~\ref{sec:uniform-weirdos} we provide a brief discussion on the
uniform distribution, where a one-step adaptive estimator with single bit
observations can achieve convergence rates faster than the familiar
$\sqrt{n}$ paramateric rate.
